### 2023-03-26 draft/draft-daniel-sanchez.tex
finish up the first draft.

\documentclass[11pt,a4paper]{article}

@@

<<setup, include = F>>=
# Load libraries

library(tidyverse)
library(patchwork)
library(lubridate)
library(knitr)
library(modelsummary)
library(fixest)
library(sandwich)

# Load the data

load('data/df-main.RData')
load('data/df18_22.RData')

# Bibliography stuff
system(paste("biber", sub("\\.Rnw$", "", current_input())))

# Predefine a graph theme

theme_ds <-
  theme_bw() +
  theme(panel.grid = element_blank(),
        text = element_text(family = 'serif', size = 10))

# Chunk options
knitr::opts_chunk$set(echo = F,
                      eval = T, 
                      warning = F, 
                      message = F)
@

% ----- Document ----- %

\begin{document}

@@

\begin{figure}[h]
\caption{Active formal businesses and job contracts registered under Social Security in Ecuador}
\label{fig:fig}
<<figure-1, fig.height= 6, fig.width= 10>>=
log_buss_country <-
  df %>% 
  filter(year %>% between(2018,2022)) %>% 
  group_by(month_year) %>% 
  summarise(buss_new = sum(buss_new)) %>% 
  ggplot(aes(month_year %>% as.Date(), log(buss_new)))+
  geom_point(size = 1)+
  geom_line()+
  scale_x_date(date_breaks = '6 months', 
               date_labels = '%b-%y') +
  geom_vline(xintercept = as.numeric(as.Date('2020-05-01')),
             colour = 'blue', 
             linetype = 'dashed') +
  theme_ds +
  labs(x = '',
       y = 'Log of active businesses',
       title = 'Business Creation',
       subtitle = 'Log of active business registered') +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5))

log_jobs_country <-
  df18_22 %>% 
  group_by(month_year) %>% 
  summarise(jobs = sum(jobs)) %>% 
  ggplot(aes(month_year %>% as.Date(), log(jobs)))+
  geom_point(size = 1)+
  geom_line()+
  scale_x_date(date_breaks = '6 months', 
               date_labels = '%b-%y') +
  geom_vline(xintercept = as.numeric(as.Date('2020-05-01')),
             colour = 'blue', 
             linetype = 'dashed') +
  theme_ds +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5)) +
  labs(x = '',
       y = 'Log of contracts',
       title = 'Employment registered under Social Security',
       subtitle = 'Log of total job contracts at the national level')

log_buss_country + 
log_jobs_country +
  plot_layout(ncol = 2) +
  plot_annotation(caption = 'Data from the Ecuadorian Companies Superintendency and from INEC (Ecuadorian National Statistics Institute).')
@
\end{figure}

@@

\section{Methodology}
\subsection{Data}
I construct a province-month panel dataset of the country with variables stemming from various government sources. The variable of interest is the log of total job contracts registered with Social Security. Table \ref{tab:sources} defines all variables used in the paper along with their source. Any kind of job contract which is registered in Social Security is thought to be formal, as Social Security formalization implies that all employment benefits mandated by the Ecuadorian Labour Code are being met by the employer and the government.
\begin{table}[h]
\caption{Mean values by year}
\label{tab:descrip}
\centering
<<descriptive, results = 'asis'>>=
# Descriptive statistics table
descrip_table <- 
  df18_22 %>% 
  transmute('Formal jobs' = log(jobs),
            'Active businesses' = log(buss_new),
            'Remote workers' = log(remote_workers),
            'Registered tax contributors' = log(registered),
            'Reported sales' = log(total_sales),
            'Total COVID-19 cases' = log(total_covid_cases),
            'Total COVID-19 deaths' = log(total_covid_dead),
            'Thefts' = log(thefts),
            'Homicides' = log(homicides),
            'Transit Accidents' = log(transit_accidents),
            'Year' = as.factor(year)) %>% 
  as.data.frame()

# Use the datasummary function from modelsummary

datasummary(All(descrip_table, factor = F) ~ (Mean * Year),
            fmt = fmt_decimal(2),
            data = descrip_table,
            output = 'latex_tabular')
@
\vspace{0.3cm}
All variables in natural log form. See Appendix A for data sources.
\end{table}
\subsection{Empirical Strategy}

@@

\section{Results}
Table \ref{tab:regseg} displays OLS estimation results for the empirical model specified in Equation \ref{eqn:seg} and Table \ref{app:seg} in Appendix B presents the same results but with HAC standard errors. Model 1 below estimates a naive segmented regression model considering only the treatment dummy interacted with the time trend. The interaction between the time trend and the treatment dummy is not statistically significant, which is evidence for a null effect of the SAS reform on employment. The negative and statistically significant coefficient on the treatment dummy means that, as time passed, there seemed to be a negative trend after the date of the policy. Model 2 estimates the same naive model but now considering province fixed effects, which control for all province-specific factors which affect formal employment yet stay constant through time. In this case, including the FE controls renders the interaction term positive and significant. Potentially, the $\hat{\delta_1}$ coefficient in Model 1 is biased toward zero as it is possible that some provinces with less economic activity suffered from staggered pandemic effects after the policy change. If other provinces saw a positive effect, it would mean that the average effect on the naive regression would be biased toward zero. 
\begin{table}[htbp!]
\caption{Segmented Regressions}
\label{tab:regseg}
<<segmented-regressions, results = 'asis'>>=
data <- 
  df18_22 %>%
  mutate(jobs = log(jobs),
         buss_new = log(buss_new),
         remote_workers = log(remote_workers),
         registered = log(registered),
         total_sales = log(total_sales),
         total_covid_cases = log(total_covid_cases),
         total_covid_dead  = log(total_covid_dead),
         thefts = log(thefts),
         homicides = log(homicides),
         transit_accidents = log(transit_accidents),
         lag_jobs = log(lag_jobs)) %>% 
  rename(provcode = 'province_code')

# Run the segmented regressions

# A naive model

naive <- feols(log(jobs) ~ time*treat ,
               cluster = ~ month_year + provcode,
               data = data)

# Fixed effects

fe1 <- feols(log(jobs) ~ time*treat | provcode,
             cluster = ~ month_year + provcode,
             data = data)

# FE with variables, not COVID-19

fe2 <- feols(log(jobs) ~ time*treat + remote_workers + thefts + homicides + registered + total_sales + transit_accidents |
               provcode,
             cluster = ~ month_year + provcode,
             data = data)

# FE with variables and a quadratic time trend, not COVID-19

fe3 <- feols(log(jobs) ~ time + I(time^2)*treat + remote_workers + thefts + homicides + registered + 
               total_sales + transit_accidents |
               provcode,
             cluster = ~ month_year + provcode,
             data = data)

# FE with a lag, businesses and quadratic time trend, no COVID-19.

fe4 <- feols(log(jobs) ~ lag_jobs + buss_new + time + I(time^2)*treat + remote_workers + thefts + homicides + registered + 
             total_sales + transit_accidents |
             provcode,
             cluster = ~ month_year + provcode,
             data = data)

# FE with variables and businesses, to see how much is controlled. With COVID-19

fe5 <- feols(log(jobs) ~ buss_new + lag_jobs + time + I(time^2)*treat + remote_workers + thefts + homicides + registered + 
               total_sales + transit_accidents + total_covid_cases + total_covid_dead | provcode,
             cluster = ~ month_year + provcode,
             data = data)

# List of models

models <- list(
  naive,
  fe1,
  fe2,
  fe3,
  fe4,
  fe5
)

# Make a table

stars <- c('*'= 0.1, '**' = 0.05, '***'= 0.01)

# Coefficient mapping

coefficient_names <-  c(
  'time' = 'Time',
  'I(time^2)' = 'Time (quadratic)',
  'treatTreatment Period' = 'Treatment',
  'time:treatTreatment Period' = 'Interaction',
  'I(time^2):treatTreatment Period' = 'Interaction (quadratic)',
  'remote_workers' = 'WFH workers',
  'thefts' = 'Thefts',
  'homicides' = 'Homicides',
  'registered' = 'Tax contributors',
  'total_sales' = 'Sales',
  'transit_accidents' = 'Transit Accidents',
  'buss_new'= 'Businesses',
  'lag_jobs' = 'Lag of jobs',
  'total_covid_cases' = 'COVID-19 cases',
  'total_covid_dead' = 'COVID-19 deaths'
)

# Goodness of fit mapping

gm <-
  list(list("raw" = "nobs", "clean" = "$N$", "fmt" = 0),
       list("raw" = "adj.r.squared", "clean" = "Adj. $R^2$", "fmt" = 5),
       list("raw" = "r2.within.adjusted", "clean" = "Adj. Within $R^2$", "fmt" = 5),
       list("raw" = "aic", "clean" = "AIC", "fmt" = 2),
       list("raw" = "bic", "clean" = "BIC", "fmt" = 2),
       list("raw" = "FE: provcode", "clean" = "Province FE", "fmt" = 0))

# Output the table

modelsummary(models,
             stars = stars,
             output = 'latex_tabular',
             coef_map = coefficient_names,
             gof_map = gm)
@
\vspace{0.3cm}
\textbf{Note:} Segmented regression models across multiple specifications. Standard errors are clustered at the month-year and province level.\\
$ *p < 0.1, **p < 0.05, ***p < 0.01.$
\end{table}
\begin{figure}[htbp!]
\caption{Event study plots}
\label{fig:event}
<<event-study, fig.width= 10>>=
# Event study graph, with the last specification and without COVID-19 data. Includes a lag.

es1 <- feols(log(jobs) ~ my_event + log(lag_jobs) + remote_workers + thefts + homicides + registered + total_sales +
               transit_accidents | provcode, 
             cluster = ~ provcode + my_event,
             data = data)

# With businesses

es2 <- feols(log(jobs) ~ my_event + log(lag_jobs) + remote_workers + thefts + homicides + registered + total_sales +
               transit_accidents + buss_new| provcode, 
             cluster = ~ provcode + my_event,
             data = data)

# With COVID-19 but no businesses

es3 <- feols(log(jobs) ~ my_event + log(lag_jobs) + remote_workers + total_covid_cases + thefts + homicides 
             + registered + total_sales + total_covid_dead + transit_accidents | provcode, 
             cluster = ~ provcode + my_event,
             data = data)

# With COVID-19 but businesses

es4 <- feols(log(jobs) ~ my_event + log(lag_jobs) + remote_workers + total_covid_cases + thefts + homicides 
             + registered + total_sales + total_covid_dead + transit_accidents + buss_new | provcode, 
             cluster = ~ provcode + my_event,
             data = data)

# List of models

es <- list(
  es1,
  es2,
  es3,
  es4
)

es_coefs <- 
  modelsummary(es,
               output = 'data.frame',
               statistic = '{std.error}',
               gof_omit  = '.*',
               fmt = 10) %>% 
  filter(substr(term, 1, 8) == 'my_event') %>%
  rename(m1 = '(1)',
         m2 = '(2)',
         m3 = '(3)',
         m4 = '(4)') %>% 
  gather(model,
         value,
         m1,
         m2,
         m3,
         m4) %>% 
  mutate(value = as.numeric(value),
         my_string = str_sub(term, 9),
         month_year = parse_date_time(my_string, orders = '%m%Y') %>% ymd(),
         statistic = if_else(statistic == '{std.error}', 'se', statistic)) %>%
  pivot_wider(names_from = statistic,
              values_from = value) %>% 
  select(-part, -term, -my_string) %>% 
  arrange(month_year)

event_study_graph1 <-
  es_coefs %>%
  filter(model == 'm1') %>% 
  ggplot(aes(month_year, estimate)) +
  geom_point(colour = '#0B6623') +
  scale_x_date(date_breaks = '6 months', 
                 date_labels = '%b-%y') +
  geom_vline(xintercept = as.numeric(as.Date('2020-05-01')),
             colour = 'blue', 
             linetype = 'dashed') +
  geom_errorbar(aes(ymin = estimate - (1.96 * se),
                    ymax = estimate + (1.96 * se)),
                width = 0.5,
                color = '#0B6623') +
  geom_hline(yintercept = 0) +
  theme_ds +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5)) +
  labs(x = '',
      y = 'Average effect magnitude',
      title = 'Event study plot, 2018-2022',
      subtitle = 'Standard controls only')

event_study_graph2 <-
es_coefs %>%
  filter(model == 'm2') %>% 
  ggplot(aes(month_year, estimate)) +
  geom_point(colour = '#0B6623') +
  scale_x_date(date_breaks = '6 months', 
               date_labels = '%b-%y') +
  geom_vline(xintercept = as.numeric(as.Date('2020-05-01')),
             colour = 'blue', 
             linetype = 'dashed') +
  geom_errorbar(aes(ymin = estimate - (1.96 * se),
                    ymax = estimate + (1.96 * se)),
                width = 0.5,
                color = '#0B6623') +
  geom_hline(yintercept = 0) +
  theme_ds +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5)) +
  labs(x = '',
       y = 'Average effect magnitude',
       title = 'Event study plot, 2018-2022',
       subtitle = 'Controlling for business creation')

event_study_graph3 <-
es_coefs %>%
  filter(model == 'm3', !(is.na(estimate))) %>% 
  ggplot(aes(month_year, estimate)) +
  geom_point(colour = '#0B6623') +
  scale_x_date(date_breaks = '4 months', 
               date_labels = '%b-%y') +
  geom_vline(xintercept = as.numeric(as.Date('2020-05-01')),
             colour = 'blue', 
             linetype = 'dashed') +
  geom_errorbar(aes(ymin = estimate - (1.96 * se),
                    ymax = estimate + (1.96 * se)),
                width = 0.5,
                color = '#0B6623') +
  geom_hline(yintercept = 0) +
  theme_ds +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5)) +
  labs(x = '',
       y = 'Average effect magnitude',
       title = 'Event study plot, 2018-2022',
       subtitle = 'Controlling for COVID-19 outcomes.' )

event_study_graph4 <-
es_coefs %>%
  filter(model == 'm4', !(is.na(estimate))) %>% 
  ggplot(aes(month_year, estimate)) +
  geom_point(colour = '#0B6623') +
  scale_x_date(date_breaks = '4 months', 
               date_labels = '%b-%y') +
  geom_vline(xintercept = as.numeric(as.Date('2020-05-01')),
             colour = 'blue', 
             linetype = 'dashed') +
  geom_errorbar(aes(ymin = estimate - (1.96 * se),
                    ymax = estimate + (1.96 * se)),
                width = 0.5,
                color = '#0B6623') +
  geom_hline(yintercept = 0) +
  theme_ds +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5)) +
  labs(x = '',
       y = 'Average effect magnitude',
       title = 'Event study plot 2020-2022',
       subtitle = 'Controlling for business creation and COVID-19 outcomes.')

event_study_graph1 + event_study_graph2 + event_study_graph3 + event_study_graph4 +
  plot_layout(ncol = 2,
              nrow = 2)
@
\textbf{Notes:} Event study plots where the coefficients of period dummies are plotted against time. The reference level is May 2020. All plots include the standard controls, which are defined in Model 3 of Table \ref{tab:regseg}. COVID-19 outcomes include total suspected COVID-19 cases and deaths, as reported by the Ecuadorian Ministry of Health.
\end{figure}

Models 3 through 5 consider a variety of controls and alternative specifications to check for the robustness of Model 2's results. Model 3 adds a variety of controls. WFH workers will control for temporary waves of COVID-19 contagions. The amount of transit accidents work to that effect as well. Further, thefts and homicides should control for any kind of effect of the recent violence wave that has stricken the country beginning 2020 and intensified during 2022. Both the amount of firm-type tax contributors and reported sales to the tax authority control for economic fluctuations. The effect is only significant when considering a quadratic trend of the time variable (Model 4), and in even in such case, the magnitude of the effect is very small: on average, the SAS reform created \Sexpr{round(fe3$coefficients['I(time^2):treatTreatment Period']*100,6)}\% more Social Security-registered jobs.

@@

<<hac-segmented, results = 'asis'>>=
modelsummary(models,
             stars = stars,
             output = 'latex_tabular',
             coef_map = coefficient_names,
             gof_map = gm,
             vcov = vcovHAC) 
@

>>>>

\documentclass[11pt,a4paper]{article}\usepackage[]{graphicx}\usepackage[]{xcolor}
% maxwidth is the original width if it is less than linewidth
% otherwise use linewidth (to make sure the graphics do not exceed the margin)
\makeatletter
\def\maxwidth{ %
  \ifdim\Gin@nat@width>\linewidth
    \linewidth
  \else
    \Gin@nat@width
  \fi
}
\makeatother

\definecolor{fgcolor}{rgb}{0.345, 0.345, 0.345}
\newcommand{\hlnum}[1]{\textcolor[rgb]{0.686,0.059,0.569}{#1}}%
\newcommand{\hlstr}[1]{\textcolor[rgb]{0.192,0.494,0.8}{#1}}%
\newcommand{\hlcom}[1]{\textcolor[rgb]{0.678,0.584,0.686}{\textit{#1}}}%
\newcommand{\hlopt}[1]{\textcolor[rgb]{0,0,0}{#1}}%
\newcommand{\hlstd}[1]{\textcolor[rgb]{0.345,0.345,0.345}{#1}}%
\newcommand{\hlkwa}[1]{\textcolor[rgb]{0.161,0.373,0.58}{\textbf{#1}}}%
\newcommand{\hlkwb}[1]{\textcolor[rgb]{0.69,0.353,0.396}{#1}}%
\newcommand{\hlkwc}[1]{\textcolor[rgb]{0.333,0.667,0.333}{#1}}%
\newcommand{\hlkwd}[1]{\textcolor[rgb]{0.737,0.353,0.396}{\textbf{#1}}}%
\let\hlipl\hlkwb

\usepackage{framed}
\makeatletter
\newenvironment{kframe}{%
 \def\at@end@of@kframe{}%
 \ifinner\ifhmode%
  \def\at@end@of@kframe{\end{minipage}}%
  \begin{minipage}{\columnwidth}%
 \fi\fi%
 \def\FrameCommand##1{\hskip\@totalleftmargin \hskip-\fboxsep
 \colorbox{shadecolor}{##1}\hskip-\fboxsep
     % There is no \\@totalrightmargin, so:
     \hskip-\linewidth \hskip-\@totalleftmargin \hskip\columnwidth}%
 \MakeFramed {\advance\hsize-\width
   \@totalleftmargin\z@ \linewidth\hsize
   \@setminipage}}%
 {\par\unskip\endMakeFramed%
 \at@end@of@kframe}
\makeatother

\definecolor{shadecolor}{rgb}{.97, .97, .97}
\definecolor{messagecolor}{rgb}{0, 0, 0}
\definecolor{warningcolor}{rgb}{1, 0, 1}
\definecolor{errorcolor}{rgb}{1, 0, 0}
\newenvironment{knitrout}{}{} % an empty environment to be redefined in TeX

\usepackage{alltt}

@@

% ----- Document ----- % 
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\begin{document}

@@

\begin{figure}[h]
\caption{Active formal businesses and job contracts registered under Social Security in Ecuador}
\label{fig:fig}
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
\includegraphics[width=\maxwidth]{figure/figure-1-1} 
\end{knitrout}
\end{figure}

@@

\section{Methodology}
\subsection{Data}
I construct a province-month panel dataset of the country with variables stemming from various government sources. The variable of interest is the log of total job contracts registered with Social Security. Table \ref{tab:sources} defines all variables used in the paper along with their source. Any kind of job contract which is registered in Social Security is thought to be formal, as Social Security formalization implies that all employment benefits mandated by the Ecuadorian Labour Code are being met by the employer and the government.
\begin{table}[h]
\caption{Mean values by year}
\label{tab:descrip}
\centering

\begin{tabular}[t]{lrrrrr}
\toprule
  & 2018 & 2019 & 2020 & 2021 & 2022\\
\midrule
Formal jobs & \num{10.24} & \num{10.23} & \num{10.16} & \num{10.08} & \num{10.14}\\
Active businesses & \num{2.24} & \num{2.52} & \num{2.42} & \num{2.84} & \num{3.05}\\
Remote workers & \num{0.93} & \num{1.37} & \num{3.15} & \num{2.37} & \num{1.79}\\
Registered tax contributors & \num{10.54} & \num{10.61} & \num{10.69} & \num{10.76} & \num{10.87}\\
Reported sales & \num{18.80} & \num{18.81} & \num{18.71} & \num{18.81} & \num{18.96}\\
Total COVID-19 cases &  &  & \num{6.41} & \num{6.47} & \num{6.43}\\
Total COVID-19 deaths &  &  & \num{2.97} & \num{2.64} & \num{1.96}\\
Thefts & \num{4.52} & \num{4.53} & \num{4.19} & \num{4.33} & \num{4.52}\\
Homicides & \num{1.05} & \num{1.11} & \num{1.19} & \num{1.38} & \num{1.81}\\
Transit Accidents & \num{1.04} & \num{1.10} & \num{1.01} & \num{0.92} & \num{1.14}\\
\bottomrule
\end{tabular}

\vspace{0.3cm}
All variables in natural log form. See Appendix A for data sources.
\end{table}
\subsection{Empirical Strategy}

@@

\section{Results}
Table \ref{tab:regseg} displays OLS estimation results for the empirical model specified in Equation \ref{eqn:seg} and Table \ref{app:seg} in Appendix B presents the same results but with HAC standard errors. Model 1 below estimates a naive segmented regression model considering only the treatment dummy interacted with the time trend. The interaction between the time trend and the treatment dummy is not statistically significant, which is evidence for a null effect of the SAS reform on employment. The negative and statistically significant coefficient on the treatment dummy means that, as time passed, there seemed to be a negative trend after the date of the policy. Model 2 estimates the same naive model but now considering province fixed effects, which control for all province-specific factors which affect formal employment yet stay constant through time. In this case, including the FE controls renders the interaction term positive and significant. Potentially, the $\hat{\delta_1}$ coefficient in Model 1 is biased toward zero as it is possible that some provinces with less economic activity suffered from staggered pandemic effects after the policy change. If other provinces saw a positive effect, it would mean that the average effect on the naive regression would be biased toward zero. 
\begin{table}[htbp!]
\caption{Segmented Regressions}
\label{tab:regseg}

\begin{tabular}[t]{lcccccc}
\toprule
  & (1) & (2) & (3) & (4) & (5) & (6)\\
\midrule
Time & \num{0.000}* & \num{0.000} & \num{0.000} & \num{0.000}*** & \num{0.000} & \num{0.000}\\
 & (\num{0.000}) & (\num{0.000}) & (\num{0.000}) & (\num{0.000}) & (\num{0.000}) & (\num{0.000})\\
Time (quadratic) &  &  &  & \num{0.000}*** & \num{0.000} & \num{0.001}***\\
 &  &  &  & (\num{0.000}) & (\num{0.000}) & \vphantom{1} (\num{0.000})\\
Treatment & \num{-0.024}*** & \num{-0.016}*** & \num{-0.011}*** & \num{-0.007}*** & \num{0.000} & \num{0.002}***\\
 & (\num{0.003}) & (\num{0.003}) & (\num{0.001}) & (\num{0.002}) & (\num{0.001}) & (\num{0.001})\\
Interaction & \num{0.000} & \num{0.000}*** & \num{0.000} &  &  & \\
 & (\num{0.000}) & (\num{0.000}) & (\num{0.000}) &  &  & \\
Interaction (quadratic) &  &  &  & \num{0.000}*** & \num{0.000} & \num{-0.001}***\\
 &  &  &  & (\num{0.000}) & (\num{0.000}) & (\num{0.000})\\
WFH workers &  &  & \num{0.000} & \num{0.000} & \num{0.000}** & \num{0.000}\\
 &  &  & (\num{0.000}) & (\num{0.000}) & (\num{0.000}) & \vphantom{2} (\num{0.000})\\
Thefts &  &  & \num{0.002} & \num{0.001} & \num{0.001}* & \num{0.000}\\
 &  &  & (\num{0.002}) & (\num{0.002}) & (\num{0.001}) & (\num{0.001})\\
Homicides &  &  & \num{0.000} & \num{0.000} & \num{0.000} & \num{0.000}\\
 &  &  & (\num{0.000}) & (\num{0.000}) & (\num{0.000}) & \vphantom{1} (\num{0.000})\\
Tax contributors &  &  & \num{-0.011} & \num{-0.012} & \num{0.000} & \num{-0.002}\\
 &  &  & (\num{0.007}) & (\num{0.008}) & (\num{0.002}) & (\num{0.001})\\
Sales &  &  & \num{0.004}** & \num{0.003}** & \num{0.001} & \num{0.000}\\
 &  &  & (\num{0.002}) & (\num{0.001}) & (\num{0.000}) & (\num{0.001})\\
Transit Accidents &  &  & \num{0.000} & \num{0.000} & \num{0.000} & \num{0.000}\\
 &  &  & (\num{0.000}) & (\num{0.000}) & (\num{0.000}) & (\num{0.000})\\
Businesses &  &  &  &  & \num{0.001}*** & \num{0.001}\\
 &  &  &  &  & (\num{0.000}) & (\num{0.000})\\
Lag of jobs &  &  &  &  & \num{0.089}*** & \num{0.080}***\\
 &  &  &  &  & (\num{0.003}) & (\num{0.006})\\
COVID-19 cases &  &  &  &  &  & \num{0.000}\\
 &  &  &  &  &  & \vphantom{1} (\num{0.000})\\
COVID-19 deaths &  &  &  &  &  & \num{0.000}\\
 &  &  &  &  &  & (\num{0.000})\\
\midrule
$N$ & \num{1327} & \num{1327} & \num{394} & \num{394} & \num{394} & \num{216}\\
Adj. $R^2$ & \num{0.00117} & \num{0.99758} & \num{0.99947} & \num{0.99953} & \num{0.99991} & \num{0.99989}\\
Adj. Within $R^2$ &  & \num{0.41197} & \num{0.71887} & \num{0.75168} & \num{0.95209} & \num{0.83333}\\
AIC & \num{-1548.18} & \num{-9517.90} & \num{-3485.56} & \num{-3533.54} & \num{-4180.01} & \num{-2257.66}\\
BIC & \num{-1527.42} & \num{-9377.75} & \num{-3374.23} & \num{-3418.22} & \num{-4056.75} & \num{-2149.66}\\
Province FE &  & X & X & X & X & X\\
\bottomrule
\end{tabular}

\vspace{0.3cm}
\textbf{Note:} Segmented regression models across multiple specifications. Standard errors are clustered at the month-year and province level.\\
$ *p < 0.1, **p < 0.05, ***p < 0.01.$
\end{table}
\begin{figure}[htbp!]
\caption{Event study plots}
\label{fig:event}
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
\includegraphics[width=\maxwidth]{figure/event-study-1} 
\end{knitrout}
\textbf{Notes:} Event study plots where the coefficients of period dummies are plotted against time. The reference level is May 2020. All plots include the standard controls, which are defined in Model 3 of Table \ref{tab:regseg}. COVID-19 outcomes include total suspected COVID-19 cases and deaths, as reported by the Ecuadorian Ministry of Health.
\end{figure}

Models 3 through 5 consider a variety of controls and alternative specifications to check for the robustness of Model 2's results. Model 3 adds a variety of controls. WFH workers will control for temporary waves of COVID-19 contagions. The amount of transit accidents work to that effect as well. Further, thefts and homicides should control for any kind of effect of the recent violence wave that has stricken the country beginning 2020 and intensified during 2022. Both the amount of firm-type tax contributors and reported sales to the tax authority control for economic fluctuations. The effect is only significant when considering a quadratic trend of the time variable (Model 4), and in even in such case, the magnitude of the effect is very small: on average, the SAS reform created 0.0041\% more Social Security-registered jobs.

@@

\begin{tabular}[t]{lcccccc}
\toprule
  & (1) & (2) & (3) & (4) & (5) & (6)\\
\midrule
Time & \num{0.000} & \num{0.000} & \num{0.000}* & \num{0.000}*** & \num{0.000} & \num{0.000}\\
 & (\num{0.001}) & (\num{0.000}) & (\num{0.000}) & (\num{0.000}) & (\num{0.000}) & (\num{0.000})\\
Time (quadratic) &  &  &  & \num{0.000}*** & \num{0.000} & \num{0.001}***\\
 &  &  &  & (\num{0.000}) & (\num{0.000}) & \vphantom{1} (\num{0.000})\\
Treatment & \num{-0.024}*** & \num{-0.016}*** & \num{-0.011}*** & \num{-0.007}*** & \num{0.000} & \num{0.002}\\
 & (\num{0.004}) & (\num{0.003}) & (\num{0.001}) & (\num{0.001}) & (\num{0.001}) & (\num{0.001})\\
Interaction & \num{0.000} & \num{0.000}*** & \num{0.000} &  &  & \\
 & (\num{0.001}) & (\num{0.000}) & (\num{0.000}) &  &  & \\
Interaction (quadratic) &  &  &  & \num{0.000}*** & \num{0.000} & \num{-0.001}***\\
 &  &  &  & (\num{0.000}) & (\num{0.000}) & (\num{0.000})\\
WFH workers &  &  & \num{0.000} & \num{0.000} & \num{0.000}*** & \num{0.000}\\
 &  &  & (\num{0.000}) & (\num{0.000}) & (\num{0.000}) & \vphantom{2} (\num{0.000})\\
Thefts &  &  & \num{0.002}* & \num{0.001} & \num{0.001}*** & \num{0.000}\\
 &  &  & (\num{0.001}) & (\num{0.001}) & (\num{0.000}) & (\num{0.001})\\
Homicides &  &  & \num{0.000} & \num{0.000} & \num{0.000} & \num{0.000}\\
 &  &  & (\num{0.000}) & (\num{0.000}) & (\num{0.000}) & \vphantom{1} (\num{0.000})\\
Tax contributors &  &  & \num{-0.011}** & \num{-0.012}** & \num{0.000} & \num{-0.002}\\
 &  &  & (\num{0.005}) & (\num{0.005}) & (\num{0.001}) & (\num{0.002})\\
Sales &  &  & \num{0.004}*** & \num{0.003}*** & \num{0.001}* & \num{0.000}\\
 &  &  & (\num{0.001}) & (\num{0.001}) & (\num{0.000}) & (\num{0.000})\\
Transit Accidents &  &  & \num{0.000} & \num{0.000} & \num{0.000} & \num{0.000}\\
 &  &  & (\num{0.000}) & (\num{0.000}) & (\num{0.000}) & (\num{0.000})\\
Businesses &  &  &  &  & \num{0.001}*** & \num{0.001}**\\
 &  &  &  &  & (\num{0.000}) & (\num{0.000})\\
Lag of jobs &  &  &  &  & \num{0.089}*** & \num{0.080}***\\
 &  &  &  &  & (\num{0.003}) & (\num{0.006})\\
COVID-19 cases &  &  &  &  &  & \num{0.000}\\
 &  &  &  &  &  & \vphantom{1} (\num{0.000})\\
COVID-19 deaths &  &  &  &  &  & \num{0.000}\\
 &  &  &  &  &  & (\num{0.000})\\
\midrule
$N$ & \num{1327} & \num{1327} & \num{394} & \num{394} & \num{394} & \num{216}\\
Adj. $R^2$ & \num{0.00117} & \num{0.99758} & \num{0.99947} & \num{0.99953} & \num{0.99991} & \num{0.99989}\\
Adj. Within $R^2$ &  & \num{0.41197} & \num{0.71887} & \num{0.75168} & \num{0.95209} & \num{0.83333}\\
AIC & \num{-1548.18} & \num{-9517.90} & \num{-3485.56} & \num{-3533.54} & \num{-4180.01} & \num{-2257.66}\\
BIC & \num{-1527.42} & \num{-9377.75} & \num{-3374.23} & \num{-3418.22} & \num{-4056.75} & \num{-2149.66}\\
Province FE &  & X & X & X & X & X\\
\bottomrule
\end{tabular}
